Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-22 ms.tex
close to a full first pass at the introduction

Both SFD/FDS99 dust temperature maps are limited to $1.3^{\circ}$ resolution 
due to their reliance on DIRBE to constrain the dust SED shape. \PLANCK's 
combination of excellent sensitivity and resolution on the Rayleigh-Jeans
side of the dust spectrum's peak allow for the construction of a full-sky dust 
temperature with near-\IRAS~angular resolution. Multiple \PLANCK-based full-sky
thermal dust model are presently available. \cite{planckdust} modeled the
\PLANCK~based dust SED from 353-3000 GHz using a single MBB model in which
beta is allowed to vary continuously at $0.5^{\circ}$ resolution. 
\cite{meisner15} applied the FDS99 two-component emission

% but say that they all still are not perfect, and we want to investigate
%     what effect swapping in the latest planck release has on the dust model
% and we also just want to have a model with data from latest Planck release,
%     which has never been done by anyone before
But none of these are yet perfect. Mention CIBA and zodi as examples from
Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
exists at all.

>>>>

Both SFD/FDS99 dust temperature maps are limited to $1.3^{\circ}$ resolution 
due to their reliance on DIRBE to constrain the dust SED shape. \PLANCK's 
combination of excellent sensitivity and resolution on the Rayleigh-Jeans
side of the dust spectrum's peak allow for the construction of a full-sky dust 
temperature with near-\IRAS~angular resolution. Multiple \PLANCK-based full-sky
thermal dust model are presently available. \cite{planckdust} modeled the
\PLANCK~based dust SED from 353-3000 GHz using a single MBB model in which
beta is allowed to vary continuously at $0.5^{\circ}$ resolution. 
\cite{meisner15} applied the FDS99 two-component model to the \PLANCK~based
dust SED from 100-3000 GHz, finding that two MBBs provided a significantly
better fit than a single MBB over this expanded frequency range.

% but say that they all still are not perfect, and we want to investigate
%     what effect swapping in the latest planck release has on the dust model
% and we also just want to have a model with data from latest Planck release,
%     which has never been done by anyone before

Even with the enhanced temperature resolution afforded by \PLANCK, 
systematic problems with both of these recent \PLANCK~based thermal dust 
emission models still remain. Further, no thermal dust emission model yet
exists based on the \PLANCK~2015 data release. Here we present an update
to the analysis of \cite{meisner15}, and create the first ever 100-3000 GHz
unpolarized thermal dust emission model based on the \PLANCK~2015 data release.
%But none of these are yet perfect. Mention CIBA and zodi as examples from
%Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
%exists at all.
